Forecasting the 2024 U.S. Presidential Election

### 2024-11-04 paper/paper.qmd
How Sample Recruited
How Sample Recruited

>>>>

Participants were recruited via the SSRS Omnibus Panel, a probability panel formed from ABS and telephone survey data. This dual approach ensured that both Internet and non-Internet users were included, minimizing online-only bias. Stratified by demographics (age, gender, race, education, region, and partisan affiliation), this process produced a balanced representation across groups. Selected participants received an email invitation with a unique link to the survey. Non-responders received up to two reminder emails, and those who opted for text notifications also received reminders. Participants received an e-gift card incentive upon survey completion.
